(require 'reftex)

(setq TeX-auto-save t)
(setq TeX-parse-self t)


(add-hook 'LaTeX-mode-hook 'latex-preview-pane-enable)
(add-hook 'latex-mode-hook 'latex-preview-pane-enable)

(setq reftex-plug-into-AUCTeX t)

;; (setq-default latex-preview-pane-multifile-mode 'auctex)

;; (add-hook 'LaTeX-mode-hook 'toggle-frame-fullscreen)
;; (add-hook 'latex-mode-hook 'toggle-frame-fullscreen)
;; (add-hook 'LaTeX-mode-hook '(fullscreen . fullboth))
;; (add-hook 'latex-mode-hook '(fullscreen . fullboth))
;; (add-hook 'LaTeX-mode-hook '(fullscreen . fullboth))
;; (add-hook 'latex-mode-hook '(fullscreen . fullboth))

(add-hook 'LaTeX-mode-hook 'turn-off-auto-fill)
(add-hook 'latex-mode-hook 'turn-off-auto-fill)

(add-hook 'LaTeX-mode-hook 'column-enforce-mode)
(add-hook 'latex-mode-hook 'column-enforce-mode)

(add-hook 'LaTeX-mode-hook 'turn-on-reftex)
(add-hook 'latex-mode-hook 'turn-on-reftex)

(setq-default latex-preview-pane-multifile-mode 'auctex)


(latex-preview-pane-enable)

(defun LaTeX-preview-pane-enable ()
   "Enable `latex-preview-pane-mode' in `latex-mode'."
   (add-hook 'LaTeX-mode-hook (lambda () (latex-preview-pane-mode 1))))
(LaTeX-preview-pane-enable)
(add-hook 'LaTeX-mode-hook 'LaTeX-preview-pane-enable)


(defun remove-electric-indent-mode ()
  (electric-indent-local-mode -1))
(add-hook 'LaTex-mode-hook 'remove-electric-indent-mode)
(add-hook 'latex-mode-hook 'remove-electric-indent-mode)

 ;; '(latex-preview-pane-multifile-mode (quote auctex))



;; '(package-selected-packages (quote (latex-preview-pane)))

;; (when (fboundp 'electric-indent-mode) (electric-indent-mode -1))
(custom-set-variables
 ;; custom-set-variables was added by Custom.
 ;; If you edit it by hand, you could mess it up, so be careful.
 ;; Your init file should contain only one such instance.
 ;; If there is more than one, they won't work right.
 '(TeX-master "convection.tex")
 )
(custom-set-faces
 ;; custom-set-faces was added by Custom.
 ;; If you edit it by hand, you could mess it up, so be careful.
 ;; Your init file should contain only one such instance.
 ;; If there is more than one, they won't work right.
 )
